---
title: "Untitled"
author: "Yash Deole 20BCE1300"
date: "`r Sys.Date()`"
output: html_document
---

```{r}
library(ggplot2)
library(dplyr)
library(DT)
library(tidyverse)
library(wordcloud)
library(tm)
library(reshape2)
```


```{r}
data=read.csv("movie_metadata.csv",header=T)
```


```{r}
#exploring our data
summary(data)
```


```{r}
#removing columes not useful to us
data2=data[,c(2:13,15,20:26)]
```

removing duplicate rows
```{r}
#removing 
data2$movie_title <- (sapply(data2$movie_title,gsub,pattern="\\Â",replacement=""))
data2$genres_2 <- (sapply(data2$genres,gsub,pattern="\\|",replacement=" "))
data2 = data2[!duplicated(data2$movie_title),]

```

removing data with no revenue column as we need to predict revenue.
imputing revenue can lead to wrong assumptions and predictions
hence to remove bias we have removed all data without gross column
```{r}
data2=data2[complete.cases(data2['gross']),]
```
we must ensure same currancy value for all countries
```{r}
data2 <- transform(data2, budget = ifelse(country == "South Korea", budget/1186.31, budget))
data2 <- transform(data2, budget = ifelse(country == "Japan", budget/111.91, budget))
data2 <- transform(data2, budget = ifelse(country == "Turkey", budget/8.86, budget))
data2 <- transform(data2, budget = ifelse(country == "Hungary", budget/309.93, budget))
data2 <- transform(data2, budget = ifelse(country == "Thailand", budget/33.93, budget))

data2 <- transform(data2, gross = ifelse(country == "South Korea", gross/1186.31, gross))
data2 <- transform(data2, gross = ifelse(country == "Japan", gross/111.91, gross))
data2 <- transform(data2, gross = ifelse(country == "Turkey", gross/8.86, gross))
data2 <- transform(data2, gross = ifelse(country == "Hungary", gross/309.93, gross))
data2 <- transform(data2, gross = ifelse(country == "Thailand", gross/33.93, gross))
```

```{r}
print(paste(sum(complete.cases(data2)),"Complete cases!"))
```

```{r}
summary(data2)
```

```{r}
#remaining na values are not removed as we want to use as much data as we can.Imputing data as director name doesn't make sense.Hence from here on forth we will remove data as or when required
```

```{r}
#decreasing the scale of budget and gross
mil=1000000
data2['budget']=data2['budget']/mil
data2['gross']=data2['gross']/mil

summary(data2['gross'])
```


```{r}
df=data2[!is.na(data['budget']),]
df["profit"]=df["gross"]-df["budget"]
df <- transform(df, profit = ifelse(profit>0, 1, 0))

df%>%
  na.omit()%>%
  ggplot(aes(imdb_score,budget,color=profit))+geom_point()+geom_jitter()

#seeing year wise imdb vs 
df%>%
  na.omit()%>%
  ggplot(aes(imdb_score,gross,color=budget))+geom_point()+facet_wrap(~profit)
#most movies with high imdb rating our profitable

#budget vs profit
df["profit"]=df["gross"]-df["budget"]

df%>%
  na.omit()%>%
  ggplot(aes(budget,profit))+geom_point()+
  geom_hline(yintercept =0,colour="steel blue")
#significant amount of movies actually arent profitable
```
Analysing negative profit movies
```{r}
neg=df[df['profit']<0,]
dim(neg)
# top movies with negative profit

neg%>%
  arrange(profit)%>%
  head(10)
```
Splitting genre from tables
```{r}

genre=c()
for(i in data2['genres_2']){
  # print(i)
  genre=c(genre,unlist(strsplit(i," ")));
}
```


```{r}
class(strsplit(data2[0,"genres_2"]," "))
```

```{r}
gen=as.data.frame(table(genre))
ggplot(gen, aes(genre, weight = Freq))+theme(axis.text.x=element_text(angle=45, hjust=1))+
         geom_bar(fill="steel blue")+
         scale_x_discrete(limits = gen$genre[order(gen$Freq,decreasing=T)])
```

```{r}
originC=as.data.frame(table(data2['country']))
ggplot(originC, aes(country, weight = Freq))+theme(axis.text.x=element_text(angle=45, hjust=1))+
         geom_bar(fill="steel blue")+
         scale_x_discrete(limits = originC$country[order(originC$Freq,decreasing=T)])

```
```{r}
#to know which if country playes any role we must calculate value acc to average revenue

originC=data2%>%group_by(country)%>%summarise(revenue=mean(gross))
ggplot(originC, aes(country, weight = revenue))+
theme(axis.text.x=element_text(angle=45, hjust=1))+
         geom_bar(fill="steel blue")+
         scale_x_discrete(limits = originC$country[order(originC$revenue,decreasing=T)])

```


```{r}
originC=data2%>%
  filter(!is.na(budget))%>%
  group_by(country)%>%summarise(avg_budget=mean(budget, na.rm=T))
ggplot(originC, aes(country, weight = avg_budget))+
theme(axis.text.x=element_text(angle=45,hjust=1))+
         geom_bar(fill="steel blue")+
         scale_x_discrete(limits = originC$country[order(originC$avg_budget,decreasing=T)])
```


```{r}
quantile(data2[!is.na(data2['imdb_score']),"imdb_score"],c(0.05,0.5,0.8,0.95))
ggplot(data2,aes(imdb_score))+
  geom_histogram(bins=80)+
  geom_vline(xintercept = mean(data2$imdb_score,na.rm = TRUE),colour="steel blue")+
  geom_vline(xintercept = quantile(data2$imdb_score, prob = c(0.05)),colour="red",linetype = "longdash")+
  geom_vline(xintercept = quantile(data2$imdb_score, prob = c(0.95)),colour="red",linetype = "longdash")+
  ylab("Count of Movies")+
  xlab("IMDB Score")+
  ggtitle("Histogram: IMDB Score")
```
Hence 95% percent of movies have imdb rating less than 8.We can classify our A listers as actors and directors who gave an average rating of 7.3 or higher
```{r}
#finding best directors and actors
df=data2[!is.na(data2['director_name']),]
df2=df%>%
  group_by(director_name)%>%
  summarise(counts=n(),avg_rate=mean(imdb_score,na.rm=T) )%>%
  arrange(desc(avg_rate))%>%
  filter(counts>4)
#we dont need directors with 1-4 movies as not enough movies produced

#top ten directors

df2[1:10,]%>%
  ggplot(aes(director_name,avg_rate))+theme(axis.text.x=element_text(angle=45, hjust=1))+geom_col(fill="springgreen")

```

```{r}
#finding demographic with most revenue as we aim to 
str(data2)
data2%>%
  group_by(content_rating)%>%
  summarise(avg_revenue=mean(gross),avg_imdb=mean(imdb_score,na.rm=T))%>%
  ggplot(aes(content_rating,avg_revenue,fill=avg_imdb))+theme(axis.text.x=element_text(angle=45, hjust=1))+geom_col()
#G PG and PG-13 are most popular hence it may and will help to boost revenue though it has lower imdb ratings

```

```{r}
data2=data2[complete.cases(data2$budget),]
```

```{r}
list=c()
for(i in 1:nrow(data2)) {
  hit_status_criteria=data2[i,17]*1.5
  if(data2[i,8]>=hit_status_criteria)
  {
    list=c(list,1)
  }
  else{
    list=c(list,0)
  }
}
data2$hit <- list
head(data2)
```

```{r}

data2%>%
  group_by(director_name)%>%
  filter(n()>5)%>%
  summarise(hit_ratio=sum(hit)/n(),likes=mean(director_facebook_likes))%>%
  ggplot(aes(director_name,hit_ratio,fill=likes))+ geom_col(stat='identity')+theme(axis.text.x=element_text(angle=45, hjust=1))

#directors with more popularity doesnt translate into better hits

```

```{r}
dataz=na.omit(data2)
dataz=dataz[,c(2,3,4,5,7,8,12,17,18,19,20,22)]
# colnames(data2)
#no null value found
#Finding correlation using heatmap
corr_mat <- round(cor(dataz),2)

# reorder corr matrix
# using corr coefficient as distance metric
dist <- as.dist((1-corr_mat)/2)

# hierarchical clustering the dist matrix
hc <- hclust(dist)
corr_mat <-corr_mat[hc$order, hc$order]
melted_corr_mat <- melt(corr_mat)

ggplot(data = melted_corr_mat, aes(x=Var1, y=Var2,fill=value)) +  geom_tile()+
  geom_text(aes(Var2, Var1, label = value),
            color = "white", size = 4)+labs(title="Corelation Matrix of given Variables")+xlab("Variables")+ylab("Variables")
```


```{r}
library(e1071)
library(caTools)
library(class)
data10=data2[c(2:5,7,12,17,18,19,20,22)]
data10=na.omit(data10)
split <- sample.split(data10, SplitRatio = 0.7)
train_cl <- subset(data10, split == "TRUE")
test_cl <- subset(data10, split == "FALSE")
  
# Feature Scaling
train_scale <- scale(train_cl[, 1:10])
test_scale <- scale(test_cl[, 1:10])
  
# Fitting KNN Model 
# to training dataset
classifier_knn <- knn(train = train_scale,test = test_scale,cl = train_cl$hit,k = 1)
  
# Confusiin Matrix
cm <- table(test_cl$hit, classifier_knn)
cm
  
# Model Evaluation - Choosing K
# Calculate out of Sample error
misClassError <- mean(classifier_knn != test_cl$hit)
print(paste('Accuracy =', 1-misClassError))
  
# K = 19
classifier_knn <- knn(train = train_scale,
                      test = test_scale,
                      cl = train_cl$hit,
                      k = 19)
misClassError <- mean(classifier_knn != test_cl$hit)
print(paste('Accuracy =', 1-misClassError))
```


```{r}
data3<- data2[c('movie_title','budget','gross','imdb_score','actor_1_facebook_likes','actor_2_facebook_likes','actor_3_facebook_likes','hit')]
data10=data2[c('budget','gross','hit')]
str(data2)
# Loading package
library(caTools)
library(randomForest)
```


```{r}
r2 = function(ytest,y_pred){
  ans = (1-sum((ytest-y_pred)^2)/sum((ytest-mean(ytest))^2))
  paste("R2 Score:",round(ans*100,2),"%")
}
head(data)

```


```{r}
data2 =na.omit(data2)
```


```{r}
library(caTools)
library(randomForest)
datak = data2[,c(2:5,7,12,17,18,19,20)]
datak$Gross = data2$gross

X = datak[,-ncol(datak)]
Y = datak[,ncol(datak)]
# # iris = datasets::iris
split <- sample.split(datak, SplitRatio = 0.7)
# split

train <- subset(datak, split == "TRUE")
test <- subset(datak, split == "FALSE")

# Fitting Random Forest to the train dataset
set.seed(120)  # Setting seed

classifier_RF = randomForest(x = X,y = Y,ntree = 500)
xtrain = train[,-ncol(datak)]
xtest = test[,-ncol(datak)]
ytest = test[,ncol(datak)]
ytrain = train[,ncol(datak)]
classifier_RF

# Predicting the Test set results
y_pred = predict(classifier_RF, newdata = xtest)

# Plotting model
plot(classifier_RF)

# Importance plot
importance(classifier_RF)

# Variable importance plot
varImpPlot(classifier_RF)

r2(ytest,y_pred)
```

```{r}
dataz=na.omit(data2)
dataz=dataz[,c(2,3,4,5,7,8,12,17,18,19,20,22)]
#no null value found
#Finding correlation using heatmap
corr_mat <- round(cor(dataz),2)

# reorder corr matrix
# using corr coefficient as distance metric
dist <- as.dist((1-corr_mat)/2)

# hierarchical clustering the dist matrix
hc <- hclust(dist)
corr_mat <-corr_mat[hc$order, hc$order]
melted_corr_mat <- melt(corr_mat)

ggplot(data = melted_corr_mat, aes(x=Var1, y=Var2,fill=value)) +  geom_tile()+
  geom_text(aes(Var2, Var1, label = value),
            color = "white", size = 4)+labs(title="Corelation Matrix of given Variables")+
  theme(axis.text.x=element_text(angle=45, hjust=1))+
  xlab("Variables")+ylab("Variables")
colnames(data)
```


